Manuscript_physiological_consequences_blood_parasite_infection

### 2022-02-10 MS_physiology_infection.Rmd
Add files via upload

@@

**Results**

@@

## plotting count of infected / uninfected nestlings across treatments

@@

## plotting mean infection intensity values of nestlings across treatments

mean_inf_int=c(mean(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Control"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Control"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Malarone"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Malarone"])), na.rm=T))

se_inf_int=c(se(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Control"]))),se(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Control"]))),se(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Malarone"]))), se(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Malarone"]))))

tab_mean=data.frame(Timepoint=c("Pre-treatment","Post-treatment","Pre-treatment","Post-treatment"),Mean_infection_intensity=mean_inf_int,se_inf_int=se_inf_int,Treatment=c("Control","Control","Malarone","Malarone"))

tab_mean$Timepoint=factor(tab_mean$Timepoint,levels = c("Pre-treatment","Post-treatment"))

@@

treatment_meaninf_changes=ggplot(mean_infint)+
  aes(Sampling_rank,Infection_intensity,group=Treatment, fill=Treatment)+
  geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color='darkgrey')+
  labs(y="Mean infection intensity")+
  # ylim(c(0,3))+
  geom_point(aes(colour=Treatment),position=position_jitterdodge(jitter.width = 0.2, jitter.height = 0.5))+  # position=position_jitterdodge()
  # geom_line(aes(group=Treatment,color=Treatment, fill=Treatment),size=2)+
  stat_summary(fun=mean, geom="line",size=2,color=c("lightgrey","black","black","lightgrey"))+
  stat_summary(fun=mean, geom="point",size=5)+
  stat_summary(geom="errorbar", width=0.04, size=2)+
  scale_color_manual(values=c("lightgrey","black"))+
  theme_classic()+
  theme(axis.title.x = element_blank(), legend.text = element_text(size=16), legend.title = element_text(size=16), axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16), plot.margin = unit(c(0,0,0,30), "pt"))

@@

# Mean infection intensity

@@

# Testing for difference in infection intensity in malarone treated nestlings before versus after treatment

@@

# Testing for difference in infection intensity in control nestlings before versus after treatment

perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint)
```

@@

```{r, echo=F}

## Summary sample sizes data

```{r}
#Summary of sample size across years

table(data2016_2020$Year)

### Number samples across infection stages

table(data2016_2020$Diff_Inf_Class)

### Average days between first and second sample

mean(data2016_2020$days_resample)

sd(data2016_2020$days_resample)

range(data2016_2020$days_resample)

### table infection prevalence in nestlings

table(data2016_2020$Prevalence)

# Infection stages as response variable

## 1) Variation of breathing rate according to infection stage

@@

@@

## 2) Variation of body temperature according to infection stage

@@

## 3) Variation of body condition according to infection stages

@@

# Plot of predicted values of body condition change among infection stages

@@

## 4) Variation of growth rate according to infection stages

@@

# Parasitemia as response variable

## 1) Variation of breathing rate according to Leucocytozoon increase, Peak or increase infection intensity

@@

mod_br_para <- mod_br_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m1)), levels=c(paste0(x,"\nn=",m1))))
mod_br_para$lower_CI=c(31.11, mod_br_para$predicted[1]-2.96, mod_br_para$predicted[1]-6.49,mod_br_para$predicted[1]-4.67, mod_br_para$predicted[1]-4.63)
mod_br_para$higher_CI=c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)

gg1_pred_para=ggplot(mod_br_para)+
  aes(as.factor(mod_br_para$x),mod_br_para$predicted)+
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  geom_errorbar(aes(ymin=mod_br_para$lower_CI,ymax=mod_br_para$higher_CI),colour="black",size=2, width=.1)+
  # geom_errorbar(aes(ymin=mod_br_para$predicted-mod_br_para$std.error,ymax=mod_br_para$predicted+mod_br_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_br_para$higher_CI, na.rm=T)+1.2, xend=5, yend=max(mod_br_para$higher_CI, na.rm=T)+1.2))+
    geom_text(aes(x=3, y=max(mod_br_para$higher_CI, na.rm=T)+2),
              label="n.s.", size = 5)
```

## 2) Variation of body temperature according to Leucocytozoon Infection_intensity and presence

@@

mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m2)), levels=c(paste0(x,"\nn=",m2))))
mod_bt_para$lower_CI=c(39.40,mod_bt_para$predicted[1]-0.40,mod_bt_para$predicted[1]-0.60,mod_bt_para$predicted[1]-0.65,mod_bt_para$predicted[1]-1.38)
mod_bt_para$higher_CI=c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))

gg2_pred_para=ggplot(mod_bt_para)+
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted)+
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm=T), linetype = "dashed")+
  geom_errorbar(aes(ymin=mod_bt_para$lower_CI,ymax=mod_bt_para$higher_CI),colour="black",size=2, width=.1)+
  labs(x="", y="Body temperature")+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bt_para$higher_CI, na.rm=T)+0.2, xend=5, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.2))+
    geom_text(aes(x=3, y=max(mod_bt_para$higher_CI, na.rm=T)+0.25),
              label="**", size = 8)+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bt_para$higher_CI, na.rm=T)+0.2, xend=1, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.05))+
  geom_segment(size = .8,
                 aes(x=5, y=max(mod_bt_para$higher_CI, na.rm=T)+0.05, xend=5, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.2))
```

## 3) Variation of body condition according to **Leucocytozoon** Infection_intensity and presence

@@

mod_bc_para <- mod_bc_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m3)), levels=c(paste0(x,"\nn=",m3))))
mod_bc_para$lower_CI=c(-65.99,mod_bc_para$predicted[1]-5.71,mod_bc_para$predicted[1]-53.27,mod_bc_para$predicted[1]-37.05,mod_bc_para$predicted[1]-71.88)
mod_bc_para$higher_CI=c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)

gg3_pred_para=ggplot(mod_bc_para)+
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted)+
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Δ Body condition")+
  geom_errorbar(aes(ymin=mod_bc_para$lower_CI,ymax=mod_bc_para$higher_CI),colour="black",size=2, width=.1)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=-105, xend=5, yend=-105))+
    geom_text(aes(x=3, y=-110),
              label="p=0.08", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=-105, xend=1, yend=-105+5))+
  geom_segment(size = .8,
                 aes(x=5, y=-105, xend=5, yend=-105+5))

@@

## 4) Variation of growth rate according to Leucocytozoon Infection_intensity and treatment:

@@

mod_gr_para <- mod_gr_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m4)), levels=c(paste0(x,"\nn=",m4))))
mod_gr_para$lower_CI=c(11.44,mod_gr_para$predicted[1]-2.22,mod_gr_para$predicted[1]-10.47,mod_gr_para$predicted[1]-6.60,mod_gr_para$predicted[1]-11.39)
mod_gr_para$higher_CI=c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)

gg4_pred_para=ggplot(mod_gr_para)+
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted)+
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_errorbar(aes(ymin=mod_gr_para$lower_CI,ymax=mod_gr_para$higher_CI),colour="black",size=2, width=.1)+
  # geom_errorbar(aes(ymin=mod_gr_para$predicted-mod_gr_para$std.error,ymax=mod_gr_para$predicted+mod_gr_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=5, xend=5, yend=5))+
    geom_text(aes(x=3, y=5-0.63),
              label="p=0.09", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=5, xend=1, yend=5+0.5))+
  geom_segment(size = .8,
                 aes(x=5, y=5, xend=5, yend=5+0.5))

@@

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "./table_results/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

@@

# Host health to parasitemia 
```{r, warning=F,message=F}

@@

# # First sampling parasitemia
# 
# ## Same with delta body condition
# 
# tol_resdata$Infection_intensity.1=as.numeric(tol_resdata$Infection_intensity.1)
# tolres_deltamod=lm(body_condition.1~Infection_intensity.1*Diff_Inf_Class, data=tol_resdata)
# 
# # comparison of slopes among infection stages 
# 
# lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.1, var="Infection_intensity.1")
# 
# contrast(lms_delta,"pairwise")
# 
# tolre_deltasum=summary(lms_delta)
# 
# # comparison of slopes to zero
# 
# summary(lms_delta, infer=T)
# 
# # body condition change - first infection intensity
# 
# tolres_delta_first=ggplot(data =data2016_2020[! data2016_2020$Infection_intensity.1 %in% NA & ! data2016_2020$Diff_Inf_Class %in% c(NA,"Uninfected"),], aes(y=body_condition.1,x=as.numeric(Infection_intensity.1),col=Diff_Inf_Class))+
#     geom_jitter(size=3, alpha=0.5)+
#     geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
#     labs(title = "First sampling", y="Body condition change",x="Parasitemia \n at first sampling", col='Infection stages')+
#     # scale_x_continuous(breaks=seq(1,5,1),labels=c("0","1","2","3","4"))+
#     scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
#     theme_classic()+
#     theme(legend.position = "none", axis.text = element_text(size=16), axis.title = element_text(size=18))

@@

@@

tolres_deltamod=lm(body_condition.2~Infection_intensity*Diff_Inf_Class, data=tol_resdata)

@@

# ## plot
# 
# tolres=ggplot(data =data2016_2020[! data2016_2020$Infection_intensity %in% c(NA,0) & ! data2016_2020$Diff_Inf_Class %in% NA,], aes(y=body_condition.2,x=as.numeric(Infection_intensity),col=Diff_Inf_Class))+
#   geom_jitter(size=3, alpha=0.5)+
#   geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
#   labs(y="Body condition \n at second sampling",x="Parasitemia \n at second sampling", col='Infection stages')+
#   scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
#   scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
#   theme_classic()+
#   theme(legend.text = element_text(size=19),legend.title = element_text(size=22), axis.text = element_text(size=16), axis.title = element_text(size=18))

# body condition change - second infection intensity

@@

# Supplementary figure

@@

gg1=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,Breathing_rate)+
  geom_hline(yintercept = mean(data2016_2020$Breathing_rate, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate (z-transformed)")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

gg2=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,body_temperature)+
  geom_hline(yintercept = mean(data2016_2020$body_temperature, na.rm=T), linetype = "dashed")+
  labs(x="", y="Body temperature (z-transformed)")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

gg3=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,delta_body_condition)+
  geom_hline(yintercept = mean(data2016_2020$delta_body_condition, na.rm=T), linetype = "dashed")+
  labs(x="", y="Body condition (z-transformed)")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

>>>>

### Setting classes of variables

@@

**Analyses**

@@

## Plotting count of infected / uninfected nestlings across treatments

@@

## Plotting mean infection intensity values of nestlings across treatments

@@

treatment_meaninf_changes=ggplot(mean_infint)+
  aes(Sampling_rank,Infection_intensity, group=Treatment)+
  geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color='darkgrey')+
  labs(y="Mean infection intensity")+
  geom_point(aes(colour=Treatment),position=position_jitterdodge(jitter.height = 0.1))+  #jitter.width = 0.2, jitter.height = 0.5) position=position_jitterdodge()
  # geom_line(aes(group=Treatment,color=Treatment, fill=Treatment),size=2)+
  stat_summary(fun=mean, geom="line",size=2,color=c("lightgrey","black","black","lightgrey"))+
  stat_summary(fun=mean, geom="point",size=5)+
  stat_summary(fun.data=mean_se, geom="errorbar", width=0.04, size=2)+
  scale_color_manual(values=c("lightgrey","black"))+
  theme_classic()+
  theme(axis.title.x = element_blank(), legend.text = element_text(size=16), legend.title = element_text(size=16), axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16), plot.margin = unit(c(0,0,0,30), "pt"))

@@

# Testing for difference in mean infection intensity between Pre and Post treatment

@@

first=mean_before_after[mean_before_after$Timepoint %in% "Pre-treatment",]

## Pre-treatment difference in parasitic load between Treatments

perm.t.test(as.numeric(as.character(first$Infection_intensity))~first$Treatment)

sd(first$Infection_intensity[first$Treatment %in% "Control"])

## In malarone treated nestlings

@@

# In control nestlings

perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint)

@@

# Infection stages as explanatory variable

## Breathing rate

@@

# Plotting predicted values across infection stages

@@

## Body temperature

@@

## Body condition change

@@

# Plotting predicted values across infection stages

@@

## Growth rate

@@

# Parasitemia as explanatory variable

## Breathing rate

@@

mod_br_para <- mod_br_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m1)), levels=c(paste0(x,"\nn=",m1))))
mod_br_para$lower_CI=c(31.11, mod_br_para$predicted[1]-2.96, mod_br_para$predicted[1]-6.49,mod_br_para$predicted[1]-4.67, mod_br_para$predicted[1]-4.63)
mod_br_para$higher_CI=c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)
mod_br_para$se=c(2.61,1.74,2.09,1.56,2.31)

# Plotting predicted values across infection intensities

gg1_pred_para=ggplot(mod_br_para)+
  aes(as.factor(mod_br_para$x),mod_br_para$predicted)+
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  geom_errorbar(aes(ymin=mod_br_para$lower_CI,ymax=mod_br_para$higher_CI),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_br_para$predicted-mod_br_para$se,ymax=mod_br_para$predicted+mod_br_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_br_para$higher_CI, na.rm=T)+1.2, xend=5, yend=max(mod_br_para$higher_CI, na.rm=T)+1.2))+
    geom_text(aes(x=3, y=max(mod_br_para$higher_CI, na.rm=T)+2),
              label="n.s.", size = 5)
```

## Body temperature

@@

mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m2)), levels=c(paste0(x,"\nn=",m2))))
mod_bt_para$lower_CI=c(39.40,mod_bt_para$predicted[1]-0.40,mod_bt_para$predicted[1]-0.60,mod_bt_para$predicted[1]-0.65,mod_bt_para$predicted[1]-1.38)
mod_bt_para$higher_CI=c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))
mod_bt_para$se=c(0.23,0.24,0.24,0.21,0.29)

# Plotting predicted values across infection intensities

gg2_pred_para=ggplot(mod_bt_para)+
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted)+
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm=T), linetype = "dashed")+
  geom_errorbar(aes(ymin=mod_bt_para$lower_CI,ymax=mod_bt_para$higher_CI),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_bt_para$predicted-mod_bt_para$se,ymax=mod_bt_para$predicted+mod_bt_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  labs(x="", y="Body temperature")+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bt_para$higher_CI, na.rm=T)+0.2, xend=5, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.2))+
    geom_text(aes(x=3, y=max(mod_bt_para$higher_CI, na.rm=T)+0.25),
              label="**", size = 8)+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bt_para$higher_CI, na.rm=T)+0.2, xend=1, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.05))+
  geom_segment(size = .8,
                 aes(x=5, y=max(mod_bt_para$higher_CI, na.rm=T)+0.05, xend=5, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.2))
```

## Body condition change

@@

mod_bc_para <- mod_bc_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m3)), levels=c(paste0(x,"\nn=",m3))))
mod_bc_para$lower_CI=c(-65.99,mod_bc_para$predicted[1]-5.71,mod_bc_para$predicted[1]-53.27,mod_bc_para$predicted[1]-37.05,mod_bc_para$predicted[1]-71.88)
mod_bc_para$higher_CI=c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)
mod_bc_para$se=c(23.20,14.57,17.69,13.51,19.29)

# Plotting predicted values across infection intensities

gg3_pred_para=ggplot(mod_bc_para)+
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted)+
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Δ Body condition")+
  geom_errorbar(aes(ymin=mod_bc_para$lower_CI,ymax=mod_bc_para$higher_CI),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_bc_para$predicted-mod_bc_para$se,ymax=mod_bc_para$predicted+mod_bc_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=-105, xend=5, yend=-105))+
    geom_text(aes(x=3, y=-110),
              label="p=0.08", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=-105, xend=1, yend=-105+5))+
  geom_segment(size = .8,
                 aes(x=5, y=-105, xend=5, yend=-105+5))

@@

## Growth rate

@@

mod_gr_para <- mod_gr_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m4)), levels=c(paste0(x,"\nn=",m4))))
mod_gr_para$lower_CI=c(11.44,mod_gr_para$predicted[1]-2.22,mod_gr_para$predicted[1]-10.47,mod_gr_para$predicted[1]-6.60,mod_gr_para$predicted[1]-11.39)
mod_gr_para$higher_CI=c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)
mod_gr_para$se=c(3.47,2.36,2.89,2.16,3.12)

# Plotting predicted values across infection intensities

gg4_pred_para=ggplot(mod_gr_para)+
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted)+
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_errorbar(aes(ymin=mod_gr_para$lower_CI,ymax=mod_gr_para$higher_CI),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_gr_para$predicted-mod_gr_para$se,ymax=mod_gr_para$predicted+mod_gr_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=5, xend=5, yend=5))+
    geom_text(aes(x=3, y=5-0.63),
              label="p=0.09", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=5, xend=1, yend=5+0.5))+
  geom_segment(size = .8,
                 aes(x=5, y=5, xend=5, yend=5+0.5))

@@

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.se = T,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "./table_results/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

@@

# Host health to parasitemia

```{r, warning=F,message=F}

@@

@@

## linear model testing effect of infection intensity at second sampling on body condition change

tolres_mod=lm(delta_body_condition~Infection_intensity, data=tol_resdata)

summary(tolres_mod)

## Testing the interaction between infection stages and infection intensities

@@

tolres_deltamod=lm(delta_body_condition~Infection_intensity*Diff_Inf_Class, data=tol_resdata)

@@

# Plotting body condition change - second infection intensity

@@

# Supplementary figures

@@

# Plotting observed values across infection stages

gg1=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,Breathing_rate)+
  geom_hline(yintercept = mean(data2016_2020$Breathing_rate, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

gg2=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,body_temperature)+
  geom_hline(yintercept = mean(data2016_2020$body_temperature, na.rm=T), linetype = "dashed")+
  labs(x="", y="Body temperature")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

gg3=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,delta_body_condition)+
  geom_hline(yintercept = mean(data2016_2020$delta_body_condition, na.rm=T), linetype = "dashed")+
  labs(x="", y="\U0394 Body condition")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))

gg4=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
  aes(Diff_Inf_Class,Growth_rate)+
  geom_hline(yintercept = mean(data2016_2020$Growth_rate, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_jitter(color ="lightgrey", size=2, width=.3)+
  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
               size=2.8 , width=0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x))+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5 ,show.legend = FALSE)+
  stat_n_text()+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
